---
title             : "Gamifying Judgments of Associative Memory"
shorttitle        : "JAM GAME"

author: 
  - name          : "Erin M. Buchanan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "901 S. National Ave, Springfield, MO, 65897"
    email         : "erinbuchanan@missouristate.edu"
  - name          : "Abigail Van Nuland"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Missouri State University"

authornote: |
  Erin M. Buchanan is an Associate Professor of Quantitative Psychology at Missouri State University, and Abigail Van Nuland is a Masters Degree candidate at Missouri State Univeristy. 

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "judgments, word association, metacognition"

#bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

We are going to write an introduction here about JAM, association, and stuff. 

1) In a traditional free association task, people guess the words...would the numbers help? (a v b)
2) In a JAM task with multiple guesses, they would normally see the words, would expect them to be able to guess better if they know it's descending order, so the D condition would match the normal JAM slope and C should be better (this answers the bounded question).
3) For the non-numbers condition, see if singles or groups are better. Shouldn't more heads be better than one?
4) For the normal JAM task, see if groups are better than singles at guessing the numbers. 

# Method

## Participants

## Material

## Procedure

four different versions 
two of the versions included single participants versus groups of participants (a and d)

### Version A

guess the words, no numbers present
three guesses wrong and we moved on
most matches a traditional free association task 

### Version B

guess the words, numbers were present
three guesses wrong and we moved on

### Version C

guess the numbers, words were in numerical order
1 guess to get it right and they were considered right if it was within five points

### Version D

guess the numbers, words were NOT in numerical order
1 guess to get it right and they were considered right if it was within five points
most matches a JAM task 

## Data analysis

Going to talk here about MLM and Log regression as the analyses of choice because they are the most appropriate. 

# Results

## Hypothesis 1
•	Version A versus B – would answer if the number helped them guess or not
o	Multilevel log regression 
o	Random: participant, word?
o	IVs: Version, Points (sort of L, M, H words)
o	DV: correct (1) versus incorrect (0)

## Hypothesis 2
•	Version C versus D – would answer if we are better if they are in order or not
o	Multilevel regression 
o	Random: participant, word?
o	IVs: Version, Points (sort of L, M, H words)
o	DV: Score they guessed 

## Hypothesis 3
•	Version A singles versus Groups
o	Multilevel log regression 
o	Random: participant, word?
o	IVs: Singles/Groups, Points (sort of L, M, H words)
o	DV: correct (1) versus incorrect (0) 

## Hypothesis 4
•	Version D singles versus Groups
o	Multilevel regression 
o	Random: participant, word?
o	IVs: Singles/groups, Points (sort of L, M, H words)
o	DV: Score they guessed 

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
